---
title: "Untitled"
author: "Boni"
date: "2022-10-16"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# First look at our dataset

In this notebook, we will look at the necessary steps required before
any machine learning takes place. It involves:

loading the data; looking at the variables in the dataset, in
particular, differentiate between numerical and categorical variables,
which need different preprocessing in most machine learning workflows;
visualizing the distribution of the variables to gain some insights into
the dataset.

```{r}
library(readr)
Train <- read_csv("../Data/Train.csv")
Test <- read_csv("../Data/Test.csv")
VariableDefinitions <- read_csv("../Data/VariableDefinitions.csv")
SampleSubmission <- read_csv("../Data/SampleSubmission.csv")
```

```{r}
head(Train)
```

```{r}
dim(Train)
```

```{r}
VariableDefinitions
```

## Data Understanding

Data understanding involves the exploration of data that includes the
use of statistics and data visualizations. Descriptive statistics can be
used to summarize the data, inferential statistics can be used to test
two data sets and samples, and regressions can be used to explore the
relationships between multiple variables. Data visualizations use
charts, graphs, and dashboards to understand the data. This phase allows
you to understand the quality of data.

```{r}
colnames(Train)
```

```{r}

```

```{r}
library(psych)
glimpse(Train)
```

```{r}
# library(explore)
# explore(Train)
```

```{r}
skimr::skim(Train)
```

```{r}
# library(ggplot2)
# ggplot(Train, aes(x = class, colour = class)) +
#   geom_linerange(aes(ymin = 	mig_year, ymax = 	mig_year)) +
#   geom_point(aes(y = 	mig_year)) +
#   # geom_point(aes(y = .to)) +
#   coord_flip() +
#   theme(legend.position = "bottom")
```

## Data Preparation

Data preparation is one of the most important and time-consuming phases
and can include selecting a sample subset or variables selection,
imputing missing values, transforming attributes or variables including
log transform and feature scaling transformation, and duplicates
removal. Variables selection can be done with a correlation matrix in a
data visualization.

```{r, warning=FALSE,message=FALSE}
library(rsample)
library(caret)
library(workflows)
library(recipes)
library(parsnip)
```

`initial_split` creates a single binary split of the data into a
training set and testing set. `initial_time_split` does the same, but
takes the first `prop` samples for training, instead of a random
selection. `group_initial_split` creates splits of the data based on
some grouping variable, so that all data in a "group" is assigned to the
same split. `training`and `testing`are used to extract the resulting
data.

```{r}
Split <- initial_split(Train,prop = 0.7,strata = income_above_limit)
TrainingSet<- training(Split)
TestingSet <- testing(Split)
```

Once a recipe is defined, it needs to be estimated before being applied
to data. Most recipe steps have specific quantities that must be
calculated or estimated. For example, `step_normalize()`needs to compute
the training set's mean for the selected columns, while
`step_dummy()`needs to determine the factor levels of selected columns
in order to make the appropriate indicator columns.

The two most common application of recipes are modeling and stand-alone
preprocessing. How the recipe is estimated depends on how it is being
used.

Modeling

```{r}
recipes <- recipe(income_above_limit~.,data = TrainingSet)%>%
  step_impute_knn(all_nominal_predictors(), neighbors = 3)%>%
    step_normalize(all_predictors()) %>%
  step_dummy(all_nominal(),-all_outcomes())%>%
  step_range(all_predictors(),-all_nominal(),max = 
               1,min = 0)
```

Note that the data passed to recipe() need not be the complete data that
will be used to train the steps (by prep()). The recipe only needs to
know the names and types of data that will be used. For large data sets,
head() could be used to pass a smaller data set to save time and memory.

```{r}
TraingSet <- recipes%>%
  prep(TrainingSet)%>%
  bake(TrainingSet)
TestingSet <- recipes%>%
  prep(TrainingSet)%>%
  bake(TrainingSet)
```

## Modeling

Modeling usually means the development of a prediction model to predict
a variable in data. The prediction model can be developed using
regression algorithms, statistical learning algorithms, and machine
learning algorithms like neural networks, support vector machines, naïve
Bayes, multiple linear regressions, decision trees, and more. You can
also build prescriptive and descriptive models.

```{r}
decision_tree_rpart_spec <-
  decision_tree(tree_depth = tune(), min_n = tune(), cost_complexity = tune()) %>%
  set_engine('rpart') %>%
  set_mode('classification')

logistic_reg_glm_spec <-
  logistic_reg() %>%
  set_engine('glm')

mlp_keras_spec <-
  mlp(hidden_units = tune(), penalty = tune(), dropout = tune(), epochs = tune(), activation = tune()) %>%
  set_engine('keras') %>%
  set_mode('classification')

naive_Bayes_naivebayes_spec <-
  naive_Bayes(smoothness = tune(), Laplace = tune()) %>%
  set_engine('naivebayes')

rand_forest_randomForest_spec <-
  rand_forest(mtry = tune(), min_n = tune()) %>%
  set_engine('randomForest') %>%
  set_mode('classification')


```

j

```{r}
decision_tree_rpart_spec <-fit(decision_tree_rpart_spec,income_above_limit~.,data = TrainingSet)
logistic_reg_glm_spec <- fit(logistic_reg_glm_spec,income_above_limit~.,data = TrainingSet)
mlp_keras_spec <- fit(mlp_keras_spec,income_above_limit~.,data = TrainingSet)
naive_Bayes_naivebayes_spec <- fit(naive_Bayes_naivebayes_spec,income_above_limit~.,data = TrainingSet)
rand_forest_randomForest_spec <- fit(rand_forest_randomForest_spec,income_above_limit~.,data = TrainingSet)
```

## Evaluation

Evaluation is one of the phases where you may use ten-fold crossover
validation techniques to evaluate the precision and recall of your
model. You may improve your model accuracy by moving back to the
previous phase to improve or prepare your data more. You may also select
the most accurate model for your requirements. You may also evaluate the
model using the business success criteria established in the beginning
stage, which is the business understanding stage. \## Deployment
Deployment is the process of using new insights and knowledge to improve
your organization or make changes to improve your organization. You may
use your prediction model to create a data product or to produce a final
report based on your models.
